\begin{thebibliography}{99}

	\bigskip
	
     \bibitem{hashtags_facebook2015}
     E. Denton, J. Weston, M. Paluri, L. Bourdev, R. Fergus. [2015]
     \textit{User Conditional Hashtag Prediction for Images}.
     Proceedings of the 21th ACM SIGKDD International Conference 
     on Knowledge Discovery and Data Mining,
     pp. 1731 -- 1740.
     
      \bibitem{hashtags_facebook2017}
      A. Veit, M. Nickel, S. Belongie, L. Maaten. [2017]
      \textit{Separating Self-Expression and Visual Content in Hashtag Supervision}.
      arXiv preprint: 1711.09825.
      11 p.
      
     \bibitem{yfcc100m}
     B. Thomee, D. A. Shamma, G. Friedland, B. Elizalde, K. Ni,
     D. Poland, D. Borth, L.-J. Li. [2016]
     \textit{Yfcc100m: The new data in multimedia research}.
     Communications of the Association for Computing Machiner (ACM),
     pp. 64 -- 73.
        
     \bibitem{harrison}
     M. Park, H. Li, J. Kim. [2016]
     \textit{HARRISON: A Benchmark on HAshtag Recommendation
     for Real-world Images in SOcial Networks}.
     arXiv preprint:1605.05054.
     11 p.
     
	 \bibitem{sundata}
	 J. Xiao, J. Hays, K. Ehinger, A. Oliva, and A. Torralba. [2010]
	 \textit{SUN Database: Large-scale Scene Recognition from Abbey to Zoo}.
	 IEEE Conference on Computer Vision and Pattern Recognition (CVPR).
	 pp. 3 -- 22.
     
     \bibitem{imagenet}
     Olga Russakovsky, Jia Deng, Hao Su, Jonathan Krause, Sanjeev Satheesh, 
     Sean Ma, Zhiheng Huang, Andrej Karpathy, Aditya Khosla, Michael Bernstein, 
     Alexander C. Berg and Li Fei-Fei. [2015]
     \textit{ImageNet Large Scale Visual Recognition Challenge}. 
     International Journal of Computer Vision (IJCV).
     pp. 211 -- 252.
     
     \bibitem{perceptron}
     F. Rosenblatt. [1957]
     \textit{The Perceptron: a perceiving and recognizing automaton}.
     Report 85–460–1, Cornell Aeronautical Laboratory.
     
     \bibitem{activations}
     C. E. Nwankpa, W. Ijomah, A. Gachagan, S. Marshall. [2018]
     \textit{Activation Functions: Comparison of Trends in
     Practice and Research for Deep Learning}.
     arXiv preprint:1811.03378.
     20 p.
     
     \bibitem{dl_nikolenko}
     C. Николенко, A. Кадурин, E. Архангельская. [2018]
     \textit{Глубокое Обучение}.
     Издательство "Питер".
     480 с.
     
     \bibitem{losses}
     K. Janocha, W. M. Czarnecki. [2017]
     \textit{On Loss Functions for Deep Neural Networks in Classification}.
     arXiv preprint: 1702.05659.
     10 p.
     	
     \bibitem{deeplearningbook}
     I. Goodfellow, Y. Bengio, A. Courville. [2016]
     \textit{Deep learning}.
     MIT press.
     653 p.

	 \bibitem{batchnorm}
	 S. Ioffe, C. Szegedy. [2015]
	 \textit{Batch Normalization: Accelerating Deep Network Training by 
	 Reducing Internal Covariate Shift}. 
	 International Conference on Machine Learning (ICML).
	 pp. 448 -- 456
	 
	 \bibitem{dropout}
	 N. Srivastava, G. Hinton, A. Krizhevsky, I. Sutskever, R. Salakhutdinov. [2014]
	 \textit{Dropout: A Simple Way to Prevent Neural Networks from Overfitting}.
	 Journal of Machine Learning Research.
	 pp. 1929 -- 1958.
	 
	 \bibitem{resnet}
	 K. He, X. Zhang, S. Ren, J. Sun. [2015]
	 \textit{Deep Residual Learning for Image Recognition}.
	 IEEE Conference on Computer Vision and Pattern Recognition (CVPR).
	 pp. 770 -- 778
	 
	 \bibitem{inception}
	 C. Szegedy et al. [2015]
	 \textit{Going deeper with convolutions}.
	 IEEE Conference on Computer Vision and Pattern Recognition (CVPR).
	 pp. 1 -- 9.
	 
	 \bibitem{vgg}
	 K. Simonyan, Andrew Zisserman. [2015]
	 \textit{Very Deep Convolutional Networks for Large-Scale Image Recognition}.
	 International Conference on Learning Representations (ICLR).
	 14 p.
	 
	 \bibitem{adam}
	 D. P. Kingma, J. L. Ba. [2015]
	 \textit{Adam: a method for stochastic optimization}.
	 International Conference on Learning Representations (ICLR).
	 15 p.
	 
	 \bibitem{cosine}
	 I. Loshchilov, F. Hutter. [2017]
	 \textit{SGDR: Stochastic gradient descent with Warm Restarts}.
	 International Conference on Learning Representations (ICLR).
	 17 p.
	 	 
	 \bibitem{annealing}
	 S. Kirpatrick, C. Gelett, M. Vecchi. [1983]
	 Optimization by simulated annealing.
	 Sceince.
	 pp. 671 -- 680.
	 
	\bibitem{em_augs}
	A. P. Dempster; N. M. Laird; D. B. Rubin. [1977]
	\textit{Maximum Likelihood from Incomplete Data via the EM Algorithm}.
	Journal of the Royal Statistical Society.
	pp. 1 -- 38.
	 
	\bibitem{augs}
	M. A. Tanner, W. H. Wong. [1987]
	\textit{The Calculation of Posterior Distributions by Data Augmentation}.
	Journal of the American Statistical Association.
	pp. 528 -- 540.
	
\end{thebibliography}
